---
title: "Prediction and analysis of the residential buildings permits"
subtitle: "Schnieder project"
author: |
    | Justine Mao, Nikita Gusarov, Tom Vieillescazes
    | \tiny{Under direction of Beatrice Roussillon and Mathias Verdiere}
shortauthor: J.Mao, N.Gusarov, T.Vieillescazes
institute: "Université Grenoble Alpes"
shortinstitute: UGA
date: "10 january 2020"
header-includes:
    - \usepackage{array}
    - \usepackage{multicol}
output: 
    beamer_presentation:
        theme: "Szeged"
        colortheme: "spruce"
        # template: Template.tex
        slide_level: 2
        # fonttheme: "structurebold"
        toc: FALSE
        # toc_depth: 1
        df_print: "kable"
        fig_width: 4
        fig_height: 2.8
        fig_caption: yes
        includes:
            in_header: Header.tex
fontsize: 11pt
# geometry: margin = 0.5in
---

```{r include = FALSE}
###################
# Setting r options
###################
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(size = "tiny")
knitr::opts_chunk$set(dpi = 600)
knitr::opts_chunk$set(fig.align = "center") 
knitr::opts_chunk$set(fig.pos = "!htbp")
# Set chunk size
def.chunk.hook  = knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = 
    function(x, options) {
        x = def.chunk.hook(x, options)
        ifelse(options$size != "normalsize", 
            paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
    })
# Global options 
options(warn = -1)
```

```{r include = FALSE}
###############
# Load packages
###############
# Data mod
require(tidyverse)
require(DataCombine)
# Plot
require(ggfortify)
require(gridExtra)
require(grid)
# Print
require(stargazer)
require(texreg)
require(xtable)
# Time series 
require(tseries)
require(forecast)
require(vars)
# Other
require(dplyr)
# require(webshot)
# require(png)
# require(magick)
options(xtable.comment = FALSE)
```

```{r include = FALSE}
###################
# Support functions
###################
# Render stargazer caption for tables on top
bot_caption = function(expr) {
    # Capture expression
    x = capture.output(expr)
    # Parsing
    cap = grep("\\\\caption", x)
    lab = grep("\\\\label", x)
    last = grep("\\\\end\\{table", x)
    # Paste results
    cat(paste(c(x[-last], x[cap], x[lab], x[last])[-c(cap, lab)], 
        collapse = "\n"), "\n")
}
```

# Introduction 

## Objectives 

- Analyse the factors influencing construction permits number.
- Elaborate a predictive model for the construction permits to be issued.

## Presentation plan 

- Litterature study presentation 
- Database construction 
- Data presentation
- Data analysis 
- Modelisation 
    - Simple OLS models 
    - Time series models 
    - Alternative models

```{r include = FALSE}
##################################################
################## Introduction ##################
##################################################
```

# Litterature

## Sources

Nous avons commencé notre étude de la littérature par la recherche des articles méthodologiques et théoriques en lien avec le sujet traité. 

Les moteurs de recherche scientifique les plus utilisés ont été :

- Science Direct 
- Google Scholar 
- Elsevier 
- SAGE journals 

```{r include = FALSE}
########################################################
################## Revu de la litérat ##################
########################################################
```

## Variables of interest 

\tiny
\begin{table}[H]
\begin{tabular}{p{6cm} | c}
\hline \\[-1.8ex]
Number of building permits postponed by one quarter (French Building Federation, 2017) & + \\
\hline
10-year OAT rate lagged by two quarters (French Building Federation, 2017) & - \\
\hline
Unemployment rate lagged by two quarters (French Building Federation, 2017) & - \\
\hline
Deadline for housing outstandings in quarter sales shifted by one quarter (French Building Federation, 2017) & - \\
\hline
Political measure (French Building Federation, 2017)
& + or - \\
\hline
Age of the population (Lindh et al, 2008) & \\
- Individus moins de 20 ans & ++ \\
- Individuals between 20 and 59 years old (National Institute for Demographic Studies, 2019) & + \\
- Individuals over the age of 75 & -  \\
\hline
Real estate prices (Essay et al, 2015) & - \\
\hline
GDP (Lindh et al, 2002) & + \\
\hline
\end{tabular}
\normalsize
\caption{Variables of interest}
\end{table}

# Database

## Data sources 

```{r include = FALSE}
##########################
# Presentation des données 
##########################
```

We construct our database using macroeconomical variables figuring in different french and international databases : 

- Eurostat
- Sit@del2
- INSEE
- OCDE

## Data already studied 

The variables that we have already presented are : 

- Number of the building permits, 
- Surface authorised for construction (not used in analysis anymore), 
- GDP,
- Long term interest rate,
- Households spendings,
- Households investments.

## Changes and advances 

We have extracted as well the following variables :

- Population part by age group :
    - less than 20 years old,
    - from 20 to 59 years old,
    - from 60 years and more.

- Proxy variables serving to capture policies changes :
    - elective cycles dummy variables,
    - political party appartainance.

- Real estate housing prices,
- Household confidence index.

```{r include = FALSE}
# Data
ydata = read.csv("../data/derived_data/df3.csv")[,-c(1:2)] %>%
    dplyr::select(year = annee, 
        GDP = PIB, 
        TdI = Taux_interet, 
        DCF_men = DepCF_men, 
        FBCF_men,
        T_NL = total_nombre_de_logements)
ddata = read.csv("../data/derived_data/demographie.csv") %>%
    dplyr::select(total = France,
        moins20 = Em20,
        mid20_59 = E20_59,
        plus60 = E60p) %>%
    mutate(moins20 = moins20/total*100,
        mid20_59 = mid20_59/total*100,
        plus60 = plus60/total*100) %>%
    dplyr::select(moins20, 
        mid20_59, 
        plus60)
pdata = read.csv("../data/derived_data/presidence.csv") 
ydata = cbind(ydata, ddata[-26,])
Xydata = cbind(ydata, pdata)
```

# Data

## Descriptive statistics

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Statistiques déscriptives : full
bot_caption(stargazer(ydata, 
    summary = TRUE, 
    header = FALSE,
    nobs = FALSE,
    covariate.labels = c(
        "Year",
        "GDP",
        "Interest rate",
        "Household spendings",
        "Household investments",
        "Number of permits",
        "Population < 20 y.o.",
        "Population 20-59 y.o.",
        "Population > 60 y.o."),
    omit.summary.stat = c("p25", "p75"),
    title = "Descriptivve statistics for annual data"))
```

\FloatBarrier

## Data transformation

In our work we prefer to operate over indiced variables.

```{r include = FALSE}
# Relative transformation
r_ydata = ydata %>%
    mutate(t = year - min(year),
        rGDP = GDP/lag(GDP),
        rTdI = TdI/lag(TdI),
        rDCFmen = DCF_men/lag(DCF_men),
        rFBCFmen = FBCF_men/lag(FBCF_men),
        rTNL = T_NL/lag(T_NL),
        rmoins20 = moins20/lag(moins20),
        rmid2059 = mid20_59/lag(mid20_59),
        rplus60 = plus60/lag(plus60)) %>%
    dplyr::select(t, rGDP, rTdI, 
        rDCFmen, rFBCFmen, 
        rTNL,
        rmoins20, rmid2059, rplus60)
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Statistiques déscriptives
bot_caption(stargazer(r_ydata, 
    summary = TRUE, 
    header = FALSE,
    nobs = FALSE,
    omit.summary.stat = c("p25", "p75", "min", "max"),
    covariate.labels = c(
        "Year",
        "GDP",
        "Interest rate",
        "Household spendings",
        "Household investments",
        "Number of permits",
        "Population < 20 y.o.",
        "Population 20-59 y.o.",
        "Population > 60 y.o."),
    title = "Descriptive statistics for transformed data"))
```

\FloatBarrier

## Graphical representation

```{r include = FALSE}
# Time data
sr_ydata = r_ydata
colnames(sr_ydata) = c(
        "Year",
        "GDP",
        "Interest rate",
        "Household spendings",
        "Household investments",
        "Number of permits",
        "Population < 20 y.o.",
        "Population 20-59 y.o.",
        "Population > 60 y.o.")
tr_ydata = ts(r_ydata, start = 1994, frequency = 1)
str_ydata = ts(sr_ydata, start = 1994, frequency = 1)
```

\FloatBarrier

```{r echo = FALSE, fig.cap = "Original data"}
# Plots
str_ydata[, -1] %>% 
    autoplot(facets = F, cex = 0.5) + 
    theme(text = element_text(size = 7)) +
    scale_colour_manual(values = c(
        "GDP" = "#2bdfff", 
        "Interest rate" = "#2b8bff",
        "Household spendings" = "#8eff2b",
        "Household investments" = "#067500",
        "Number of permits" = "#f52707",
        "Population < 20 y.o." = "#f569e9",
        "Population 20-59 y.o." = "#f507cd",
        "Population > 60 y.o." = "#70006e"))
```

\FloatBarrier

## Political changes 

```{r include = FALSE}
# Relative transformation
Xydata = ydata %>%
    mutate(t = year,
        rGDP = GDP/lag(GDP),
        rTdI = TdI/lag(TdI),
        rDCFmen = DCF_men/lag(DCF_men),
        rFBCFmen = FBCF_men/lag(FBCF_men),
        rTNL = T_NL/lag(T_NL),
        rmoins20 = moins20/lag(moins20),
        rmid2059 = mid20_59/lag(mid20_59),
        rplus60 = plus60/lag(plus60)) %>%
    dplyr::select(t, rGDP, rTdI, 
        rDCFmen, rFBCFmen, 
        rTNL,
        rmoins20, rmid2059, rplus60)
```

\FloatBarrier

```{r echo = FALSE, fig.cap = "Original data"}
    # "GDP" = "#2bdfff", 
    # "Interest rate" = "#2b8bff",
    # "Household spendings" = "#8eff2b",
    # "Household investments" = "#067500",
    # "Number of permits" = "#f52707",
    # "Population < 20 y.o." = "#f569e9",
    # "Population 20-59 y.o." = "#f507cd",
    # "Population > 60 y.o." = "#70006e"
# Plots
Xydata %>% 
    ggplot(aes(y = rTNL, x = t, col = "Number of permits")) + 
    geom_path() + 
    geom_path(aes(y = rFBCFmen, x = t, 
        col = "Household investments")) + 
    geom_path(aes(y = rDCFmen, x = t, 
        col = "Household expenditure")) +
    geom_path(aes(y = rTdI, x = t, 
        col = "Interest rate")) +
    geom_path(aes(y = rGDP, x = t, 
        col = "GDP"), col = "#2bdfff") +
    geom_segment(aes(x = 1995, y = 0, xend = 1995, yend = 2, 
        col = "Presidential change")) +
    geom_segment(aes(x = 2007, y = 0, xend = 2007, yend = 2, 
        col = "Presidential change")) +
    geom_segment(aes(x = 2012, y = 0, xend = 2012, yend = 2, 
        col = "Presidential change")) +
    geom_segment(aes(x = 2017, y = 0, xend = 2017, yend = 2, 
        col = "Presidential change")) +
    geom_segment(aes(x = 1995, y = 0, xend = 1995, yend = 2, 
        col = "Political border change"),
        linetype="dotted",
        size = 3) +
    geom_segment(aes(x = 2012, y = 0, xend = 2012, yend = 2, 
        col = "Political border change"),
        linetype="dotted",
        size = 3) +
    geom_segment(aes(x = 2017, y = 0, xend = 2017, yend = 2, 
        col = "Political border change"),
        linetype="dotted",
        size = 3) +
    xlab("Index") + ylab("Year") +
    theme(text = element_text(size = 7))
```

\FloatBarrier

## Different housing types

```{r include = FALSE}
ydataX = read.csv("../data/derived_data/df3.csv")[,-c(1:2)] %>%
    dplyr::select(
        T_NL = total_nombre_de_logements,
        NL_pure = nombre_de_logements_autorises_individuels_purs,
        NL_groupped = nombre_de_logements_autorises_individuels_groupes,
        NL_collect = nombre_de_logements_autorises_collectifs,
        NL_resid = nombre_de_logements_autorises_en_residence) 
ydataX2 = ydataX %>%
    mutate( 
        T_NL = T_NL/ydataX[1,]$T_NL, 
        NL_pure = NL_pure/ydataX[1,]$NL_pure, 
        NL_groupped = NL_groupped/ydataX[1,]$NL_groupped, 
        NL_collect = NL_collect/ydataX[1,]$NL_collect, 
        NL_resid = NL_resid/ydataX[1,]$NL_resid)
colnames(ydataX) = c("Total number",
    "Detached", "Groupped", 
    "Collectif", "Residence")
colnames(ydataX2) = c("Total number",
    "Detached", "Groupped", 
    "Collectif", "Residence")
ts_ydataX = ts(ydataX, start = 1994, frequency = 1)
ts_ydataX2 = ts(ydataX2, start = 1994, frequency = 1)
```

\FloatBarrier

```{r echo = FALSE, resultats = "asis", fig.cap = "Construction permits by housing type"}
ts_ydataX %>% 
    autoplot() +
    scale_colour_manual(values = c(
        "Total number" = "red",
        "Detached" = "green", 
        "Groupped" = "green4", 
        "Collectif" = "blue", 
        "Residence" = "black"))
```

\FloatBarrier

## Transformed data for different housing types

\FloatBarrier

```{r echo = FALSE, resultats = "asis", fig.cap = "Construction permits by housing type, index"}
ts_ydataX2 %>% 
    autoplot() +
    scale_colour_manual(values = c(
        "Total number" = "red",
        "Detached" = "green", 
        "Groupped" = "green4", 
        "Collectif" = "blue", 
        "Residence" = "black"))
```

\FloatBarrier

# Data analysis 

## Analysis

We are going to procede in this section as follows :

- Cross-corelation study,
- Autocorrelation study,
- Partial autocorrelation study.

This analysis will be effectuated over the integrity of variables.

## Cross-correlation study

In order to verify stationarity we use the following tests :

- augmented Dickey-Fuller test (ADF), which makes it possible to test the hypothesis of the non-stationarity of a time series;
- Kwiatkowski-Phillips-Schmidt-Shin test (KPSS) to check stationarity on trend (KPSS-T) or level (KPSS-L).

These two tests allow us to verify the hypothesis of the stationarity of the series studied and, if necessary, correct it by applying a transformation on the series in question.

## Stationarity tests 

```{r include = FALSE}
# Testing
ftest = data.frame("ADF" = NA, "KPSS-T" = NA, "KPSS-L" = NA)
# ADF test
for (i in 2:(ncol(tr_ydata))) {
    ftest[i-1, 1] = adf.test(na.omit(tr_ydata[,i]))$p.val
}
for (i in 2:(ncol(tr_ydata))) {
    ftest[i-1, 2] = kpss.test(na.omit(tr_ydata[,i]),
        null = "Trend")$p.val
}
for (i in 2:(ncol(tr_ydata))) {
    ftest[i-1, 3] = kpss.test(na.omit(tr_ydata[,i]),
        null = "Level")$p.val
}
rownames(ftest) = c(
        "GDP",
        "Interest rate",
        "Household spendings",
        "Household investments",
        "Number of permits",
        "Population < 20 y.o.",
        "Population 20-59 y.o.",
        "Population > 60 y.o.")
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Results
print(xtable(ftest,
    caption = "Stationarity tests, p-values"),
    caption.placement = "bottom")
```

\FloatBarrier

## Differenced data

```{r include = FALSE}
# Data transformation
tr_ydata_diff = diff(tr_ydata)
str_ydata_diff = diff(str_ydata)
```

\FloatBarrier

```{r echo = FALSE, fig.cap = "Differenced time series"}
# Plots
str_ydata_diff[, -1] %>% 
    autoplot(facets = FALSE, cex = 0.5) + 
    theme(text = element_text(size = 7)) +
    scale_colour_manual(values = c(
        "GDP" = "#2bdfff", 
        "Interest rate" = "#2b8bff",
        "Household spendings" = "#8eff2b",
        "Household investments" = "#067500",
        "Number of permits" = "#f52707",
        "Population < 20 y.o." = "#f569e9",
        "Population 20-59 y.o." = "#f507cd",
        "Population > 60 y.o." = "#70006e"))
```

\FloatBarrier

## Stationarity reverification

```{r include = FALSE}
# Testing
ftest_diff = data.frame("ADF" = NA, "KPSS-T" = NA, "KPSS-L" = NA)
# ADF test
for (i in 2:(ncol(str_ydata_diff))) {
    ftest_diff[i-1, 1] = adf.test(na.omit(str_ydata_diff[-1,i]))$p.val
}
for (i in 2:(ncol(str_ydata_diff))) {
    ftest_diff[i-1, 2] = kpss.test(na.omit(str_ydata_diff[-1,i]),
        null = "Trend")$p.val
}
for (i in 2:(ncol(str_ydata_diff))) {
    ftest_diff[i-1, 3] = kpss.test(na.omit(str_ydata_diff[-1,i]),
        null = "Level")$p.val
}
rownames(ftest_diff) = c(
        "GDP",
        "Interest rate",
        "Household spendings",
        "Household investments",
        "Number of permits",
        "Population < 20 y.o.",
        "Population 20-59 y.o.",
        "Population > 60 y.o.")
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Results
print(xtable(ftest_diff,
    caption = "Stationarity tests, p-values"),
    caption.placement = "bottom")
```

\FloatBarrier

## Cross-correlation study

\FloatBarrier

```{r echo = FALSE, fig.cap = "Cross-correlation"}
# Data choice
par(mfrow = c(2,2), cex = 0.4)
ccf(str_ydata_diff[-1,2], str_ydata_diff[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "GDP",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
ccf(str_ydata_diff[-1,3], str_ydata_diff[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Interest rate",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3,
    na.action = na.pass)
ccf(str_ydata_diff[-1,4], str_ydata_diff[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Household spendings",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
ccf(str_ydata_diff[-1,5], str_ydata_diff[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Household investments",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
```

\FloatBarrier

## Autocorrelation

\FloatBarrier

```{r echo = FALSE, fig.cap = "Autocorrelation"}
# Data choice
par(mfrow = c(2,2), cex = 0.4)
acf(str_ydata_diff[-1,2], 
    main = "GDP",
    ylim = c(-1,1),
    cex = 0.3)
acf(str_ydata_diff[-1,3], 
    main = "Interest rate",
    ylim = c(-1,1),
    cex = 0.3,
    na.action = na.pass)
acf(str_ydata_diff[-1,4],
    main = "Household spendings",
    ylim = c(-1,1),
    cex = 0.3)
acf(str_ydata_diff[-1,5], 
    main = "Household investments",
    ylim = c(-1,1),
    cex = 0.3)
```

## Partial autocorrelation

\FloatBarrier

```{r echo = FALSE, fig.cap = "Partial autocorrelation"}
# Data choice
par(mfrow = c(2,2), cex = 0.4)
pacf(str_ydata_diff[-1,2], 
    main = "GDP",
    ylim = c(-1,1),
    cex = 0.3)
pacf(str_ydata_diff[-1,3], 
    main = "Interest rate",
    ylim = c(-1,1),
    cex = 0.3,
    na.action = na.pass)
pacf(str_ydata_diff[-1,4],
    main = "Household spendings",
    ylim = c(-1,1),
    cex = 0.3)
pacf(str_ydata_diff[-1,5], 
    main = "Household investments",
    ylim = c(-1,1),
    cex = 0.3)
```

\FloatBarrier

# Modelisation 

```{r include = FALSE}
##############
# Linear model 
##############
```

## Different models

- Simple linear models (OLS),
- Time series models (ARIMA),
- Adcanced time series vector models (VAR),
- Alternative linear models, accounting for causality effects.

## Model comparison

\tiny
\begin{table}[H]
\begin{tabular}{p{2cm} | p{4cm} | p{4cm}}
\hline \\[-1.8ex]
Model & 
    Advantages & 
        Disadvantages \\
\hline
OLS & 
    Simple to implement & 
        Unable to predict future values without acces to exogenous variables values in future \\
\hline
ARIMA & 
    Relatively simple  
    Allows to predict future values for several periods &
        \makecell{Does not take into account supplimentary information \\
        Requires stationary time series data} \\
\hline
VAR & 
    Even longer prediction horizon & 
        \makecell{Multiple restriction on data structure : \\
        - Stationarity, \\
        - No cointegration.} \\
\hline
OLS and causality & 
    \makecell{Gives predictions for short intervals (1 or 2 periods) \\
    No limiting restrictions on the data used} &
        Only short-term predictions are possible \\
\hline
\end{tabular}
\normalsize
\caption{Different models' specification}
\end{table}

# Linear models

## OLS estimations 

In this part we explore direct links between varibales without wausality imlications.

```{r include = FALSE}
# Formulas
formulas = list()
formulas[[1]] = rTNL ~ rGDP
formulas[[2]] = rTNL ~ rGDP + rTdI
formulas[[3]] = rTNL ~ rGDP + rDCFmen + rFBCFmen
formulas[[4]] = rTNL ~ rGDP + rDCFmen + rFBCFmen + rTdI
formulas[[5]] = rTNL ~ rGDP + rDCFmen + rFBCFmen + rTdI + t
``` 

```{r include = FALSE}
# Modélisation OLS
ols = list()
ols[[1]] = lm(formulas[[1]], r_ydata)
ols[[2]] = lm(formulas[[2]], r_ydata)
ols[[3]] = lm(formulas[[3]], r_ydata)
ols[[4]] = lm(formulas[[4]], r_ydata)
ols[[5]] = lm(formulas[[5]], r_ydata)
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Resultats
texreg(float.pos = "!htbp", 
    ols, 
    custom.coef.map = list(
        "rGDP" = "GDP",
        "rTdI" = "Interest rate",
        "rDCFmen" = "Household spendings",
        "rFBCFmen" = "Household investments",
        "t" = "Time"),
    caption = "OLS models comparison")
```

\FloatBarrier 

# Time series 

```{r include = FALSE}
####################
# Time series models 
####################
```

## Time series presentation

```{r include = FALSE}
# Resultats
tsTNL = diff(ts(r_ydata$rTNL, start = 1994, frequency = 1))
```

\FloatBarrier

```{r echo = FALSE, fig.cap = "Descriptive graphics"}
# Graphiques 
tsTNLX = tsTNL
p1 = autoplot(tsTNL, cex = 0.5) + 
    ylab("First differences") + 
    theme(text = element_text(size = 5)) + 
    ggtitle("Building permits number")
tsTNLd = diff(tsTNL, lag = 1, difference = 1)
p2 = autoplot(tsTNLd, cex = 0.5) + 
    ylab("Second differences") + 
    theme(text = element_text(size = 5)) + 
    ggtitle("Building permits number")
p3 = ggAcf(tsTNLX, cex = 0.5) +
        ggtitle("ACF") +
        xlab("Lag") + 
    theme(text = element_text(size = 5))
p4 = ggPacf(tsTNLX, cex = 0.5) +
        ggtitle("PACF") +
        xlab("Lag") + 
    theme(text = element_text(size = 5))
grid.arrange(p1, p2, p3, p4, nrow = 2)
```

\FloatBarrier

## ARMA modelisation

```{r include = FALSE}
tsarma = list()
tsarma[[1]] = arima(tsTNL, order = c(1, 0, 0))
tsarma[[2]] = arima(tsTNL, order = c(0, 0, 1))
tsarma[[3]] = arima(tsTNL, order = c(1, 0, 1))
tsarma[[4]] = arima(tsTNL, order = c(1, 0, 2))
tsarma[[5]] = arima(tsTNL, order = c(2, 0, 2))
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Resultats
texreg(float.pos = "!htbp", 
    tsarma, 
    custom.coef.names = c(
        "ar1" = "AR(1)", 
        "ar2" = "AR(2)",
        "Intercept" = "Intercept",
        "ma1" = "MA(1)", 
        "ma2" = "MA(2)"),
    custom.model.names = c("ARMA(1,0)",
        "ARMA(0,1)", "ARMA(1,1)", "ARMA(1,2)",
        "ARMA(2,2)"),
    caption = "Comparaison des modèles ARMA")
```

\FloatBarrier

# Vector models

```{r include = FALSE}
####################
# Time series models 
####################
```

## VAR modelisation

```{r include = FALSE}
# # Data 
# var_data = tr_ydata_diff[-nrow(tr_ydata_diff), -c(1)]
# # Models 
# tsvar = list()
# tsvar[[1]] = VAR(var_data, p = 1, 
#     type = "none")
# tsvar[[2]] = VAR(var_data, p = 2, 
#     type = "none")
```

\FloatBarrier

```{r echo = FALSE, results = "asis"}
# Resultats
# texreg(float.pos = "!htbp", 
#     tsvar[[1]]$varres, 
#     custom.coef.names = c(
#         "rGDP.l1" = "GDP(-1)", 
#         "rTdI.l1" = "I Rate(-1)",
#         "rDCFmen.l1" = "DCF(-1)",
#         "rFBCFmen.l1" = "FBFC(-1)", 
#         "rTNL.l1" = "N Permits(-1)",
#         "rmoins20.l1" = "< 20(-1)",
#         "rmid2059.l1" = "20-59(-1)"),
#     custom.model.names = c(
#         "GDP",
#         "I Rate",
#         "DCF",
#         "FBFC",
#         "N Permits",
#         "< 20", 
#         "20-59",
#         "> 60"),
#     caption = "VAR(1) results")
```

\FloatBarrier

# Alternatives

## Review of cross-correlations, part 1

\FloatBarrier

```{r echo = FALSE, fig.cap = "Cross-correlation"}
# Data choice
par(mfrow = c(2,2), cex = 0.4)
ccf(str_ydata[-1,2], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "GDP",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
ccf(str_ydata[-1,3], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Interest rate",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3,
    na.action = na.pass)
ccf(str_ydata[-1,4], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Household spendings",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
ccf(str_ydata[-1,5], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Household investments",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
```

\FloatBarrier

## Review of cross-correlations, part 2

\FloatBarrier

```{r echo = FALSE, fig.cap = "Cross-correlation"}
# Data choice
par(mfrow = c(2,2), cex = 0.4)
ccf(str_ydata[-1,7], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Population < 20",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
ccf(str_ydata[-1,8], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Population 20-59",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3,
    na.action = na.pass)
ccf(str_ydata[-1,9], str_ydata[-1,6], 
    lag.max = 5,
    type = "correlation",
    main = "Populqtion > 60",
    ylab = "Cross-correlation",
    ylim = c(-1,1),
    cex = 0.3)
```

\FloatBarrier

# Conclusion 

## Proceedings 

- Separate study of different permits types,
- Alternative linear regression implementation (that is similar to ARDL),
- Study of trimestrial data,
- Rapport finalisation,
- Delivrables preparation :
    - Excel automated model, 
    - Final rapport, 
    - R code organisation,
    - Database documentation.